The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-16 analysis/paper/paper.qmd
Update script with stop words functions

emu_theses |> 
  find_meta_stopwords(convert_to_regex = FALSE)

emu_theses |> 
  urbanism_stopwords()

stop_words_custom <- emu_theses %>% 
  unnest_tokens(output = word, input = title) %>%   ### add words from the title
  select(word) %>% 
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis", 
                               "source", "author"))) %>% 
  # rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(output = word, input = text) %>%   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") %>%  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

>>>>

meta_stopwords <- find_meta_stopwords(emu_theses, convert_to_regex = FALSE)
urbanism_stopwords <- urbanism_stopwords() 
thesis_stopwords <- thesis_stopwords()

emu_theses_words <- emu_theses |> 
  select(title, text) |>  
  unnest_tokens(output = word, input = text) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |> 
  anti_join(urbanism_stopwords, by = "word") |> 
  anti_join(thesis_stopwords, by = "word")
```
